Data Wrangling and Statistical Analysis of Assessment of Abundance, Aggregation, and Web Placement of *Agelenopsis pennsylvanica*

### 2023-03-22 data_analysis.Rmd
More edits from reviewer comments

nb_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
  geom_jitter(aes(color = Location), alpha = 0.5, width = 0.1) +
    geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Neighbor, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
  xlab("Nearest Neighbors") +
  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(legend.position = "none")

@@

main_row1 <- ggarrange(nb_plot_search, nb_plot_webs, nb_plot_spiders, labels = c("a", "b", "c"), nrow = 1, font.label = list(size = 10))
main_row2 <- ggarrange(nb_plot_dist, nb_plot_height, blankPlot, labels = c("d", "e", ""), nrow = 1, font.label = list(size = 10))

@@

```{r landscape_table}
rownames(land_cover) <- c("Area (sq. km)", "Tree Cover (%)", "Impervious Cover (%)", "Urban Cover (%)", "Urban, High Intensity (%)", "Urban, Medium Intensity (%)", "Urban, low Intensity (%)", "Urban, Open Space (%)", "Forest Cover (%)", "Deciduous Forest (%)", "Mixed Forest (%)", "Evergreen Forest (%)", "Woody Wetlands (%)", "Other Cover (%)", "Herbaceous Wetlands (%)", "Grassland Herbaceous (%)", "Pasture (%)", "Cultivated Crop (%)", "Open Water (%)")
names <- rownames(land_cover)
rownames(land_cover) <- seq(1:nrow(land_cover))
land_cover <- cbind(names, land_cover)
colnames(land_cover) <- c(" ", "Urban Center \n(UNL City Campus)", "Urban Forest \n(Wilderness Park)", "Lincoln City Limits")
flextable(land_cover[ ,1:4]) %>% 
  autofit() %>% 
  hline(i = c("3", "4", "8", "9", "13", "14"), part = "body") %>% 
  bg(i = c("4", "9", "14"), bg = "grey95") %>% 
  bold(bold = TRUE, part = "header") %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "center", part = "all") %>% 
  set_caption("") %>% 
  save_as_image(path = here::here("manuscript/figures/landscape.png"))
```

@@

flextable(pred_table_nb[ , 1:9]) %>% 
  autofit() %>% 
  merge_v(j = c('Variable', 'Model', 'McFadden\'s \nR²', 'AICc \nWeight'), part = "body") %>% 
  bold(bold = TRUE, part = "header") %>% 
  hline_bottom(part = "body", border = officer::fp_border(width = 2)) %>% 
  border(j = 'Variable', border.bottom = officer::fp_border(width = 2)) %>% 
  hline(i = c("4", "8", "11"), part = "body", border = officer::fp_border(width = 2)) %>%     
  fontsize(size = 10, part = "all") %>% 
  align(align = "center", part = "all") %>% 
  valign(valign = "top", part = "all") %>% 
  set_caption("") %>% 
  footnote(i = c(1:3, 5:7, 9, 12:14), j = 3, value = as_paragraph(
    c("Predictors that were natural log-transformed prior to model evaluation. Estimate and standard errors are not back transformed.")), 
    ref_symbols = c("a"), part = "body") %>% 
      footnote(i = 15, j = 3, value = as_paragraph(
    c("Total road Length was scaled (without centering) by dividing each value of road length by the root mean square prior to model evaluation to avoid model convergence issues.")),
    ref_symbols = c("b"), part = "body") %>% 
    footnote(i = 16, j = 3, value = as_paragraph(
    c("Tree cover is assessed as proportion (value from 0 to 1) rather than a percent (values 0 to 100) to avoid model convergence issues.")), 
    ref_symbols = c("c"), part = "body") %>% 
  save_as_image(path = here::here("manuscript/figures/pred_table_nb.png"))
```

@@

```{r land_plots}
land_plots <- ggarrange(search_land_plot, ggarrange(webs_land_plot, spiders_land_plot, dist_land_plot, height_land_plot, labels = c("b", "c", "d", "e"), ncol = 2, nrow = 2, legend = "none", align = "hv"), labels = c("a"), widths = c(0.3, 0.7))

@@

pred_table_avg_nb <- pred_table_avg_nb %>% 
  mutate(Variable = factor(Variable),
         Variable = fct_recode(Variable, "Number of Webs" = "NumWebs",
                               "Nearest Neighbor Distance" = "RetreatDist",
                               "Web Height" = "RetreatHeight"),
         Predictor = factor(Predictor),
         Predictor = fct_recode(Predictor, "Plant Species Richness" = "plant",
                                "Road-Traffic Impact" = "tdr",
                                "Highway-Traffic Impact" = "tdh",
                                "Patch Area" = "patch",
                                "Total Road Length" = "road",
                                "Spectral Radiance" = "spec",
                                "Percent Tree Cover" = "tree",
                                "Proportion Tree Cover" = "tree_frac",
                                "Spectral Radiance (Scaled)" = "spec_scale",
                                "Total Road Length (Scaled)" = "road_scale"),
         Model = factor(Model), 
         Model = fct_recode(Model, "Center " = "Center2"),
         Estimate = round(Estimate, 3),
         SE = round(SE, 3),
         Z = round(Z, 3),
         P = round(P, 3),
         AICc = round(AICc, 3))

@@

```{r land_stats}
Variable <- c("Search Distance", "Number of Webs", "Number of Spiders", "Neares Neighbor Distance", "Web Height")
Chi <- c(6.37, 19.134, 10.913, 40.757, 12.569)
df <- c("4, 21", "4, 21", "4, 21", "4, 20", "4, 130")
P <- c("  0.173", "< 0.001 ***", "  0.028 *", "< 0.001 ***", "  0.014 *")
land_stats <- data.frame(Variable, Chi, df, P)
colnames(land_stats) <- c('Variable','Likelihood Ratio \nChi-Squared','Degrees of Freedom', 'P-Value')

>>>>

nb_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
  geom_jitter(aes(color = Location), alpha = 0.5, width = 0.1) +
    geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Neighbor, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(-50, 1050), breaks = c(0, 200, 400, 600, 800, 1000)) +
  xlab("Nearest Neighbors") +
  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(legend.position = "none")

@@

main_row1 <- ggarrange(nb_plot_webs, nb_plot_spiders, blankPlot, labels = c("a", "b", ""), nrow = 1, font.label = list(size = 10))
main_row2 <- ggarrange(nb_plot_search, nb_plot_dist, nb_plot_height, labels = c("c", "d", "e"), nrow = 1, font.label = list(size = 10))

@@

```{r landscape_table}
rownames(land_cover) <- c("Area (sq. km)", "Tree Cover (%)", "Impervious Cover (%)", "Urban Cover (%)", "Urban, High Intensity (%)", "Urban, Medium Intensity (%)", "Urban, Low Intensity (%)", "Urban, Open Space (%)", "Forest Cover (%)", "Deciduous Forest (%)", "Mixed Forest (%)", "Evergreen Forest (%)", "Woody Wetlands (%)", "Other Cover (%)", "Herbaceous Wetlands (%)", "Grassland Herbaceous (%)", "Pasture (%)", "Cultivated Crop (%)", "Open Water (%)")
names <- rownames(land_cover)
rownames(land_cover) <- seq(1:nrow(land_cover))
land_cover <- cbind(names, land_cover)
colnames(land_cover) <- c(" ", "Urban Center \n(UNL City Campus)", "Urban Forest \n(Wilderness Park)", "Lincoln City Limits")
flextable(land_cover[ ,1:4]) %>% 
  autofit() %>% 
  hline(i = c("3", "4", "8", "9", "13", "14"), part = "body") %>% 
  bg(i = c("4", "9", "14"), bg = "grey95") %>% 
  bold(bold = TRUE, part = "header") %>% 
  fontsize(size = 10, part = "all") %>% 
  align(align = "center", part = "all") %>% 
  set_caption("") %>% 
  save_as_image(path = here::here("manuscript/figures/landscape.png"))
```

@@

flextable(pred_table_nb[ , 1:9]) %>% 
  autofit() %>% 
  merge_v(j = c('Variable', 'Model', 'McFadden\'s \nR²', 'AICc \nWeight'), part = "body") %>% 
  bold(bold = TRUE, part = "header") %>% 
  hline_bottom(part = "body", border = officer::fp_border(width = 2)) %>% 
  border(j = 'Variable', border.bottom = officer::fp_border(width = 2)) %>% 
  hline(i = c("4", "8", "11"), part = "body", border = officer::fp_border(width = 2)) %>%     
  fontsize(size = 10, part = "all") %>% 
  align(align = "center", part = "all") %>% 
  valign(valign = "top", part = "all") %>% 
  set_caption("") %>% 
  footnote(i = c(1:3, 5:7, 9, 12:14), j = 3, value = as_paragraph(
    c("Predictors that were natural log-transformed prior to model evaluation. Estimate and standard errors are not back transformed.")), 
    ref_symbols = c("a"), part = "body") %>% 
      footnote(i = 15, j = 3, value = as_paragraph(
    c("Total road length was scaled (without centering) by dividing each value of road length by the root mean square prior to model evaluation to avoid model convergence issues.")),
    ref_symbols = c("b"), part = "body") %>% 
    footnote(i = 16, j = 3, value = as_paragraph(
    c("Tree cover is assessed as proportion (value from 0 to 1) rather than a percent (values 0 to 100) to avoid model convergence issues.")), 
    ref_symbols = c("c"), part = "body") %>% 
  save_as_image(path = here::here("manuscript/figures/pred_table_nb.png"))
```

@@

```{r land_plots}
library("gridExtra")
library("cowplot")

land_plots <- ggarrange(search_land_plot, ggarrange(webs_land_plot, spiders_land_plot, dist_land_plot, height_land_plot, labels = c("b", "c", "d", "e"), ncol = 2, nrow = 2, legend = "none", align = "hv"), labels = c("a"), widths = c(0.3, 0.7))

gt <- arrangeGrob(webs_land_plot, spiders_land_plot,
             search_land_plot, dist_land_plot, 
             height_land_plot,
             ncol = 3, nrow = 2, 
             layout_matrix = rbind(c(1, 2, 5), c(3, 4, 5)))

land_plots <- as_ggplot(gt) +                                # transform to a ggplot
  draw_plot_label(label = c("a", "c", "b", "d", "e"), size = 15,
                  x = c(0, 0, 0.33, 0.33, 0.66), y = c(1, 0.5, 1, 0.5, 1))

@@

pred_table_avg_nb <- pred_table_avg_nb %>% 
  mutate(Variable = factor(Variable),
         Variable = fct_recode(Variable, "Number of Webs" = "NumWebs",
                               "Number of Spiders" = "NumSpiders",
                               "Nearest Neighbor Distance" = "RetreatDist",
                               "Web Height" = "RetreatHeight"),
         Predictor = factor(Predictor),
         Predictor = fct_recode(Predictor, "Plant Species Richness" = "plant",
                                "Road-Traffic Impact" = "tdr",
                                "Highway-Traffic Impact" = "tdh",
                                "Patch Area" = "patch",
                                "Total Road Length" = "road",
                                "Spectral Radiance" = "spec",
                                "Percent Tree Cover" = "tree",
                                "Proportion Tree Cover" = "tree_frac",
                                "Spectral Radiance (Scaled)" = "spec_scale",
                                "Total Road Length (Scaled)" = "road_scale"),
         Model = factor(Model), 
         Model = fct_recode(Model, "Center " = "Center2"),
         Estimate = round(Estimate, 3),
         SE = round(SE, 3),
         Z = round(Z, 3),
         P = round(P, 3),
         AICc = round(AICc, 3))

@@

```{r land_stats}
Variable <- c("Number of Webs", "Number of Spiders", "Search Distance", "Neares Neighbor Distance", "Web Height")
Chi <- c(19.134, 10.913, 6.37, 40.757, 12.569)
df <- c("4, 21", "4, 21", "4, 21", "4, 20", "4, 130")
P <- c("< 0.001 ***", "  0.028 *", "  0.173", "< 0.001 ***", "  0.014 *")
land_stats <- data.frame(Variable, Chi, df, P)
colnames(land_stats) <- c('Variable','Likelihood Ratio \nChi-Squared','Degrees of Freedom', 'P-Value')
